--- 
title: "Temperature Monitoring Project Documentation"
site: bookdown::bookdown_site
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, comment=NA, fig.align='center', cache=TRUE)
```


*** 

# Files Combination

*** 

## Overview

This section combines the two raw temperature data files from the **Time in Motion** experiment into one complete raw dataset.

```{r, echo = TRUE, class.source="fold-show"}
# Load any R packages you need here
library(ggplot2)
library(gridExtra)
library(BB)
library(VGAM)
library(fitdistrplus)
library(tidyverse)
library(gridExtra)
library(splines)
library(dplyr)
library(plotly)
library(latex2exp)
library(AcceptanceSampling)
library(png)
library(knitr)
library(scam)
```

## Input Files 

The following two raw temperature data files are used:

  * *Time_In_Motion_temperature_data.csv*

    covers the time range from 2025-07-14 08:00:00 am to 2025-08-01 07:59:00 am
    
```{r, echo = TRUE, results = 'hide', class.source="fold-show"}
#Load the 1st data file
df_temp_pre <- read.csv("data/raw/Time_In_Motion_temperature_data.csv")
#time stamp standardization
df_temp_pre <- df_temp_pre |> 
  mutate(time_stamp=floor_date(as.POSIXct(timestamp,
                                          tryFormats=c("%Y-%m-%d %H:%M:%OS")),
                               unit="minute"))
summary(df_temp_pre)
```


  * *RR_Data_temperature_Aug_to_October.csv*

    covers the time range from 2025-08-01 08:00:00 am to 2025-10-03 09:46:00 am

```{r, echo = TRUE, results = 'hide', class.source="fold-show"}
#Load the 2nd data file
df_temp <- read.csv("data/raw/RR_Data_temperature_Aug_to_October.csv")
#time stamp standardization
df_temp <- df_temp |> 
  mutate(time_stamp=floor_date(as.POSIXct(timestamp,
                                          tryFormats=c("%Y-%m-%d %H:%M:%OS")),
                               unit="minute"))
summary(df_temp)
```


## Output File

The output file of this section is:

* *Time_in_Motion_temperature_complete.csv* 
  
  * the complete raw temperature dataset for the **Time in Motion** experiment and covers the time range from 2025-07-14 08:00:00 am to 2025-10-03 09:46:00 am

```{r, echo = TRUE, results = 'hide', class.source="fold-show"}
#combine two datasets into one to do further analysis
df_temp_all <- bind_rows(df_temp_pre, df_temp) |>
  arrange(SystemID, time_stamp)
summary(df_temp_all)

#save as the whole Time in Motion dataset as a CSV file and name is: Time_in_Motion_temperature_complete.csv (option)
#write.csv(df_temp_all, "data/raw/Time_in_Motion_temperature_complete.csv", row.names = FALSE)

#read the whole dataset from the new file, just for checking (option)
#df_temp_new <- read.csv("data/raw/Time_in_Motion_temperature_complete.csv")
#summary(df_temp_new)
```


### Variables in the Output File

The complete raw temperature dataset contains the following variables:

- `SystemID`: original numeric reactor system identifier, recorded as values from $1$ to $40$
- `timestamp`: original recorded timestamp
- `reactor_temperature`: recorded reactor temperature
- `time_stamp`: standardized timestamp rounded down to the nearest minute




